Supplemental Materials, Methods and Results

### 2021-06-01 supp.Rmd
Supp now ready, just need Fig4

<!-- \renewcommand{\thefigure}{S\arabic{figure}} -->
<!-- \setcounter{figure}{0} -->
<!-- \renewcommand{\thetable}{S\arabic{table}} -->
<!-- \setcounter{table}{0} -->
<!-- \renewcommand{\theequation}{S\arabic{equation}} -->
<!-- \setcounter{equation}{0} -->

@@

<!-- ```{r tablehyp_prd, tab.align = 'center', tab.cap = "Hypotheses and associated predictions tested in this paper in relation to the population of interest, the receiver visual system used in visual modelling, and the background against which the contrast of the signal was calculated for chromatic and achromatic contrast "} -->
<!--  hyp <-  read.csv(file = "./output/tables/Table_hyp_pred.csv") -->

<!--   # Table -->
<!--  hyp2 <- flextable(hyp) %>% table_style12() -->

<!--  hyp2 -->
<!-- ``` -->

@@

<!-- ```{r Figcolsig, fig.align = 'center', fig.cap = "Additional examples of chameleon color signals and behavior in response to different social contexts. (A) Two different males in conspicuous display color adopted at the start of a contest and retained by the dominant male. (B) Two examples of males engaged in horn locking. Males in the bottom plane are evenly matched at this stage and both are in full display colour. In the top image, the male on the left is starting to change to a subordinate color. (C) Conspicuous lemon-yellow male courtship color. In this case, the female is using a contrasting stress color consistent with rejection."} -->
<!-- figs1 <- image_read("./output/figures/FigS1.png") -->
<!-- figs1 -->

<!-- ```{r Figcolsig2, fig.align = 'center', fig.cap = "Representative photos of habitat in Hawaii (A, B) and Kenya (C, D). In both sites, chameleons favored well-vegetated trees and bushes, often with lots of vines."} -->
<!-- figs2 <- image_read("./output/figures/FigS2.png") -->
<!-- figs2 -->

@@

<!-- ```{r Figcolsig3, fig.align = 'center', fig.cap = "The experimental setup for behavioral trials. We constructed a platform of three connected horizontal perches in a triangle, thereby always allowing an individual to escape a rival or if a female, a courting male."} -->
<!-- figs3 <- image_read("./output/figures/FigS3.png") -->
<!-- figs3 -->

>>>>

@@

We provided an expanded table of hypotheses and associated predictions. We also identify the data needed to test these predictions.

```{r tablehyp, tab.cap = "Hypotheses and associated predictions tested in this paper in relation to the population of interest, the receiver visual system used in visual modelling, and the background against which the contrast of the signal was calculated for chromatic and achromatic contrast."}
  source("./R/func.R") 
  hyp <-  read.csv(file = "./output/tables/Table_hyp_pred.csv")

  # Table
  hyp2 <- flextable(hyp) %>% table_style12()

  hyp2
```

@@

```{r Figcolsig, fig.align = 'center', fig.cap = "Additional examples of chameleon color signals and behavior in response to different social contexts. (A) Two different males in conspicuous display color adopted at the start of a contest and retained by the dominant male. (B) Two examples of males engaged in horn locking. Males in the bottom plane are evenly matched at this stage and both are in full display colour. In the top image, the male on the left is starting to change to a subordinate color. (C) Conspicuous lemon-yellow male courtship color. In this case, the female is using a contrasting stress color consistent with rejection."}
figs1 <- image_read("./output/figures/FigS1.png")
figs1

```{r Figcolsig2, fig.align = 'center', fig.cap = "Representative photos of habitat in Hawaii (A, C) and Kenya (B, D). In both sites, chameleons favored well-vegetated trees and bushes, often with lots of vines."}
figs2 <- image_read("./output/figures/FigS2.png")
figs2

@@

```{r Figcolsig3, fig.align = 'center', fig.cap = "The experimental setup for behavioral trials. We constructed a platform of three connected horizontal perches in a triangle, thereby always allowing an individual to escape a rival or if a female, a courting male."}
figs3 <- image_read("./output/figures/FigS3.jpg")
figs3
